Follow-up Samples

### 2017-01-25 submission/manuscript_outline_20161024.Rmd
update time analysis

loadLibs(c("dplyr", "ggplot2", "reshape2", "gridExtra", "scales", "wesanderson", "knitr", "rmarkdown"))

@@

# initial microbiome and FIT description data 
change_summary <- read.csv('../results/tables/change_theta_fit_summary.csv', header = T, row.names = 1)
alpha_summary <- read.csv('../results/tables/alpha_table_summary.csv', header = T, row.names = 1)
beta_summary <- read.csv('../results/tables/beta_diver_summary.csv', header = T, row.names = 1)
time_pvalues <- read.csv("../results/tables/time_pvalues.csv", header = T, row.names = 1)
all_OTU_pair_wilcox <- read.csv("../results/tables/OTU_paired_wilcoxson_test.csv", header = T)

@@

***Treatment and Time Differences***
There was no difference in the amount of change in positive probability for either the full or reduced lesion model for either chemotherapy (P-value = `r format(chemo_rad_summary['chemo_les', 'bh'], digits = 3)` and `r format(chemo_rad_summary['chemo_red_les', 'bh'], digits = 3)`) or radiation therapy (P-value = `r format(chemo_rad_summary['rad_les', 'bh'], digits = 3)` and `r format(chemo_rad_summary['rad_red_les', 'bh'], digits = 3)`). Although the before sample model was similar there was a significant decrease in positive probability for those treated with chemotherapy (P-value = `r format(chemo_rad_summary['chemo_IF', 'bh'], scientific = TRUE, digits = 3)` and `r format(chemo_rad_summary['chemo_red_IF', 'bh'], scientific = TRUE, digits = 3)`).  Time elapsed between the collection of the follow up sample from the initial sample, did not have a significant difference between adenoma and carcinoma (uncorrected P-value = `r format(time_pvalues["thetayc_change", "uncorrected_p_value"], digits = 3)`).

>>>>

loadLibs(c("dplyr", "reshape2", "scales", "knitr", "rmarkdown"))

@@

# initial microbiome and FIT description data 
change_summary <- read.csv('../results/tables/change_theta_fit_summary.csv', header = T, row.names = 1)
alpha_summary <- read.csv('../results/tables/alpha_table_summary.csv', header = T, row.names = 1)
beta_summary <- read.csv('../results/tables/beta_diver_summary.csv', header = T, row.names = 1)
time_pvalues <- read.csv("../results/tables/time_pvalues.csv", header = T, row.names = 1)
time_summary <- read.csv("../results/tables/time_summary_data.csv", header = T, row.names = 1)
all_OTU_pair_wilcox <- read.csv("../results/tables/OTU_paired_wilcoxson_test.csv", header = T)

@@

***Treatment and Time Differences***
There was no difference in the amount of change in positive probability for either the full or reduced lesion model for either chemotherapy (P-value = `r format(chemo_rad_summary['chemo_les', 'bh'], digits = 3)` and `r format(chemo_rad_summary['chemo_red_les', 'bh'], digits = 3)`) or radiation therapy (P-value = `r format(chemo_rad_summary['rad_les', 'bh'], digits = 3)` and `r format(chemo_rad_summary['rad_red_les', 'bh'], digits = 3)`). Although the before sample model was similar there was a significant decrease in positive probability for those treated with chemotherapy (P-value = `r format(chemo_rad_summary['chemo_IF', 'bh'], scientific = TRUE, digits = 3)` and `r format(chemo_rad_summary['chemo_red_IF', 'bh'], scientific = TRUE, digits = 3)`).  There was a significant difference in time elapsed in the collection of the follow up sample between adenoma and carcinoma samples (uncorrected P-value = `r format(time_pvalues["time", "uncorrected_p_value"], scientific = TRUE, digits = 3)`) with time passed being lower for adenoma (`r format(time_summary['adenoma', 'mean_days'], digits = 3)` +/- `r format(time_summary['adenoma', 'sd_days'], digits = 3)` days) then carcinoma (`r format(time_summary['carcinoma', 'mean_days'], digits = 3)` +/- `r format(time_summary['carcinoma', 'sd_days'], digits = 3)` days).

### 2017-01-25 submission/manuscript_outline_20161024.tex
update time analysis

\textbf{\emph{Treatment and Time Differences}} There was no difference
in the amount of change in positive probability for either the full or
reduced lesion model for either chemotherapy (P-value = 0.821 and 0.821)
or radiation therapy (P-value = 0.69 and 0.981). Although the before
sample model was similar there was a significant decrease in positive
probability for those treated with chemotherapy (P-value = 7.04e-04 and
5.07e-03). Time elapsed between the collection of the follow up sample
from the initial sample, did not have a significant difference between
adenoma and carcinoma (uncorrected P-value = 0.784).

>>>>

\textbf{\emph{Treatment and Time Differences}} There was no difference
in the amount of change in positive probability for either the full or
reduced lesion model for either chemotherapy (P-value = 0.821 and 0.821)
or radiation therapy (P-value = 0.69 and 0.981). Although the before
sample model was similar there was a significant decrease in positive
probability for those treated with chemotherapy (P-value = 7.04e-04 and
5.07e-03). There was a significant difference in time elapsed in the
collection of the follow up sample between adenoma and carcinoma samples
(uncorrected P-value = 7.59e-05) with time passed being lower for
adenoma (253 +/- 41.3 days) then carcinoma (351 +/- 102 days).
